On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-02-24 AvdMomZvolA_examples/ips_examples.tex
[AMZAE] Add one more peculiar example

For convenience, we use the notation \cite{our-ped-2018,our-pmm-2018,our-vmmsh-2018}:
$\sqrt{p}/q * \{ (x_1,y_1), ...,$ $ (x_n, y_n)  \}$,
which means that each abscissa is multiplied by $1/q$
and each ordinate is multiplied by $\sqrt{p}/q$,  i.e.
$$
	\sqrt{p}/q * \{ (x_1,y_1), ..., (x_n, y_n)  \}
	=
	\left\{ \left(\frac{x_1}{q},\frac{y_1\sqrt{p}}{q}\right), ..., \left(\frac{x_n}{q},   \frac{y_n\sqrt{p}}{q}\right)  \right\}
	.
$$
Here $q$ is the characteristic of the PIPS;
every PIPS can be represented in such way~\cite{our-vmmsh-2018-translit}[Theorem 4].

@@

>>>>

For convenience, we use the notation \cite{our-ped-2018,our-pmm-2018,our-vmmsh-2018}:
$\sqrt{p}/q * \{ (x_1,y_1), ...,$ $ (x_n, y_n)  \}$,
which means that each abscissa is multiplied by $1/q$
and each ordinate is multiplied by $\sqrt{p}/q$,  i.e.
\begin{equation}
	\label{eq:char_lattice}
	\sqrt{p}/q * \{ (x_1,y_1), ..., (x_n, y_n)  \}
	=
	\left\{ \left(\frac{x_1}{q},\frac{y_1\sqrt{p}}{q}\right), ..., \left(\frac{x_n}{q},   \frac{y_n\sqrt{p}}{q}\right)  \right\}
	.
\end{equation}
Here $q$ is the characteristic of the PIPS;
every PIPS can be represented in such way~\cite{our-vmmsh-2018-translit}[Theorem 4].

@@

The set shown on Figure~\ref{8_2400_42_56f3} has an axis of symmetry, but it is $y$ axis, not $x$ axis
and due to the fact that its characteristic is not 1,
the set cannot be rotated by $90^\circ$ but still stay on lattice~\eqref{eq:char_lattice}:
\begin{equation}
	\mathcal{P}_{8y}=
	\sqrt{42}/1*\{( \pm1200 ; 0);
	( \pm529 ; 182);
	( \pm814 ; 152);
	( \pm440 ; 80)
	\}
\end{equation}

\begin{figure}[h!]
	\center{\includegraphics[width=1\linewidth]{./img/8_2400_42_56f33d8dc5df552595e807c438bc0f55_other.png}}
	\parbox{1\linewidth}{\caption{IPS of cardinality 8 and diameter 2400}
	\label{8_2400_42_56f3}}
\end{figure}
